Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta-analysis

### 2019-11-05 manuscript/manuscript.Rmd
source meta-analysis function from github

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(qwraps2)
library(knitr)
```

```{r meta-function, echo=FALSE}
meta <-  function(Te,V_T){
m <- length(Te)
wt_FE <- 1/V_T
T_FE <- sum(Te*wt_FE)/sum(wt_FE)
Q <- sum(wt_FE*(Te - T_FE)^2)
S1 <- sum(wt_FE)
S2 <- sum(wt_FE^2)
o2 <- (Q - (m - 1))/(S1 - S2/S1)
wt_RE <- 1/(V_T + o2)
T_RE <- sum(Te*wt_RE)/sum(wt_RE)
V_T_RE_mod <- 1/sum(wt_RE)
V_T_RE_rve <- (m/(m-1))*sum(wt_RE^2*(Te - T_RE)^2)/(sum(wt_RE))^2
c(m,T_RE,o2,V_T_RE_mod, V_T_RE_rve)
}
loa_maker <- function(bias,V_bias,logs2,V_logs2) {
bias_row=meta(bias, V_bias)
logs2_row=meta(logs2, V_logs2)
bias_mean <- bias_row[2]
sd2_est <- exp(logs2_row[2])
tau_est <- bias_row[3]
LOA_L <- bias_mean - 2*sqrt(sd2_est + tau_est)
LOA_U <- bias_mean + 2*sqrt(sd2_est + tau_est)
m <- bias_row[1]
tcrit <- qt(1-.05/2,m-1)
B1 <- sd2_est^2/(sd2_est + tau_est)
B2 <- tau_est^2/(sd2_est + tau_est)
wt <- 1/V_bias
S1 <- sum(wt)
S2 <- sum(wt^2)
S3 <- sum(wt^3)
A0 <- 2*(m-1)/(S1-S2/S1)^2
A1 <- 4/(S1 - S2/S1)
A2 <- 2*(S2-2*S3/S1+S2^2/S1^2)/(S1-S2/S1)^2
V_logT2 <- A0/tau_est^2 + A1/tau_est + A2
V_logT2 <- 2/sum((V_bias + tau_est)^(-2))
V_LOA_mod <- bias_row[4] + B1*logs2_row[4] + B2*V_logT2
V_LOA_rve <- bias_row[5] + B1*logs2_row[5] + B2*V_logT2
CI_L_mod <- LOA_L - tcrit*sqrt(V_LOA_mod)
CI_U_mod <- LOA_U + tcrit*sqrt(V_LOA_mod)
CI_L_rve <- LOA_L - tcrit*sqrt(V_LOA_rve)
CI_U_rve <- LOA_U + tcrit*sqrt(V_LOA_rve)
data.frame(m, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_mod, CI_U_mod, CI_L_rve, CI_U_rve)
}
```

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=2)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m)
out

>>>>

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(qwraps2)
library(knitr)
library(bama)
```

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- bama::loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=2)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m)
out
